### 2024-02-21 documentation/thesis/thesis_document.tex
.

The Figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
summarizes this result. The plot of the raw measured values is
represented on the left. The value of the determined \emph{GoG} \(\mu\)T
values is plotted on ten individual measured values. It can be seen that
there are measured values with larger deviations (see measurement plots
\emph{7:0},\emph{10-2:0},\emph{10-1:0} in Figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}).

@@

Also, the Figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
illustrates, the measured values are plotted as a result of the filter
algorithm. As the \emph{IP\_return\_count} parameter is set to four,
only the four most similar measurements are exported. It can be seen
from the plotted \emph{\gls{cog}} \(\mu\)T deviation values, that these
are closest to an ideal Magnet with a CoG value of 0\(\mu\)T. This ideal
value is calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (magnet type, dimensions, sensor distance) as
they correspond to the mechanical structure of the used hardware sensor
in chapter \ref{d-full-sphere}.

@@

The filter algorithm implemented by the user is thus successfully
executed using the user-programmable pipeline. The calculation result is
successfully verified using raw measurement data and the result of the
algorithm.

@@

In the previous chapter \emph{Use Case Evaluation}
\ref{use-case-evaluation} it is demonstrated that the implementation of
the hardware and software framework for various magnetic field sensors
is successfully implemented.

In addition, the basic application by the user is demonstrated based on
an example. Based on this it is possible to systematically characterise
magnets from the software and readout hardware side by means of data
acquisition, storage and analysis.

After discussing the developed hardware and software components in
particular, the following chapter answers the question of whether the
selected sensors meet the requirements:

>>>>

@@

The Figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
shows the measured values filtered by the implemented filter algorithm
of Listing \ref{lst:custom_find_similar_values_algorithm}. It can be
seen that of the initial \emph{10} measurements (upper plot), only four
measurements that are most similar to the \emph{\gls{cog}} mean value
were filtered (lower plot). The number of desired result measurements
was defined here by the parameter \emph{IP\_return\_count}. It can be
seen from the plotted \emph{\gls{cog}} \(\mu\)T mean values values, that
these are closest to an ideal Magnet with a \emph{\gls{cog}} value of
0\(\mu\)T. This ideal value is calculated with the function
\emph{MRP.MRPSimulation.generate\_simulated\_reading}, with the same
measurement parameters (\emph{magnet type}, \emph{dimensions},
\emph{sensor distance}) as they correspond to the mechanical structure
of the used hardware sensor in chapter \ref{d-full-sphere}.

It can be seen that there are measured magnets with larger deviations
(see magnet index plots for \emph{7:0},\emph{10-2:0},\emph{10-1:0} in
Figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}).

@@

The filter algorithm implemented by the user is thus successfully
executed via the user-programmable pipeline The calculation result was
successfully verified using raw measurement data and the result of the
algorithm and verified using reference measurements. The streamlined
pipeline approach enables the user to re-execute the implemented
measurement pipeline example with further measurement data. Changes to
filter parameters, for example, are also possible without having to
adapt the code. Using this example, all the required functional
capabilities from the chapter \emph{Use cases} \ref{use-cases} of this
implemented solution were demonstrated in their functional capability.

@@

In the previous chapter \emph{Use Case Evaluation}
\ref{use-case-evaluation} it is demonstrated that the implementation of
the hardware and software framework for various magnetic field sensors
is successfully implemented. In addition, the basic application of the
framework for the user and the resulting advantages are demonstrated
using the specific example.

Based on this it is possible to systematically characterise magnets from
the software and readout hardware side by means of data acquisition,
storage and analysis.

After the hardware and software components developed have been discussed
in detail, the following chapter answers the question of which sensors
fulfill the requirements described in chapter
\ref{research-question-and-approach}:
